Simulating dynein's powerstroke using Brownian dynamics

### 2017-05-03 thesis/latex/thesis.tex
Thesis: change abstract to be more detailed+informative, but also more complicated. It'll need some simplificaiton.

\textbf{Abstract}
\blockquote{Dynein is a motor protein which uses cellular energy to transport cargo around the cell. Like related motor proteins kinesin and myosin, dynein uses ATP bond breaking to alternatingly kick its two foot domains forward and generate motion. Unlike the more regularly-stepping kinesin or myosin, dynein's stepping pattern is very random: it can take steps between zero and 60\textit{nm} in both the forwards and backwards directions. It is believed that dynein takes broad, stochastic steps because it is large and has several elastic regions, making it more affected by Brownian motion. To test this, we model the motor as a 2D system of springy hinges, then simulate this model using Brownian dynamics. Preliminary results indicate such a model is capable of taking steps between 0 and 25nm. These results give hope that, with further tweaking, the model may be able to generate both larger and backwards steps.}

>>>>

\textbf{Abstract}
\blockquote{Dynein is a motor protein which transports cargo along tracks inside the cell. Like related motor proteins kinesin and myosin, dynein uses cellular energy to take steps with its two foot domains. Unlike the more regularly-stepping kinesin or myosin, dynein's stepping pattern is very random: it can take steps between zero and 60\textit{nm} in both the forwards and backwards directions. It is believed that dynein takes such broad, stochastic steps because of its large size and several elastic regions, which make it more influenced by Brownian motion. To test this diffusion-dominated hypothesis for dynein stepping, we create a minimal model of dynein with elastic regions which feels Brownian forces, and simulate the model's stepping behavior in a cellular environment. The model treats dynein's domains as ``point hinges'' connected by rigid rods, and accomplishes steps by changing the openness of its hinges. The model's behavior is found using Brownian dynamics equations. Preliminary data indicate such a model is capable of taking steps between 0 and 25nm. These results affirm that the Brownian hinge model of dynein is capable of stepping, and give hope that, with further tweaking, the model may be able to generate both larger and backwards steps, supporting the notion of a diffusion-dominated dynein step.}
